\section{Experience}
  \subsection{Vocational}
    \cventry{2014--2016}{Web Developer}{AgendaPro}{http://www.agendapro.co}{Santiago}{Management system and online bookings for small and medium companies.\newline{}%
      Full-stack development in Ruby on Rails, using jQuery and Twitter Bootstrap. Principal developed modules:%
      \begin{itemize}%
        \item \textit{Workflow} for online booking, including a view to see available hours.
        \item Multiple services for the same booking and an \textit{Optimizer Hours} to find the best time to do all the services.
        \item e-Mail system for notification of new or modified bookings, and reminders.
        \item Clients management:
          \begin{itemize}%
            \item Booking hystory and profile.
            \item Search and filter clients.
            \item Promotional e-mails to clients.
          \end{itemize}
        \item Search engine for locala, services, and service providers.
      \end{itemize}
    }
    \cventry{2012--2014}{Web Developer}{ICCSolutions}{Santiago}{}{Software factory of Universidad de los Andes\newline{}%
      Develope of software by order based on Web2Py:
      \begin{description}
        \item[FAI] Management system and resources control for the departament of \textit{Investigación y Desarrollo}.
        \item[IngUandes] Webpage of courses for \textit{Facultad de Ingeniería y Ciencias aplicadas}. Developed modules:
          \begin{itemize}
            \item Web postulation, report submision, and evaluation of an internship.
            \item Submision of counsil letters.
            \item Postulation to assistantships.
          \end{itemize}
        \item[SAF] Adaptation of \textit{IngUandes} to use it in other faculties and new modules developed.
      \end{description}
    }
  \subsection{Miscellaneous}
    \cventry{2011--2013}{Corrector Assistant}{Facultad de Ingeniería y Ciencias aplicadas}{Santiago}{}{Test and assigments checker of the course \textit{Introducción a la Programación}.}
    \cventry{2013 Second Semester}{Assistant Professor}{Facultad de Ingeniería y Ciencias aplicadas}{Santiago}{}{Assistant Professor of the course \textit{Introducción a la Programación}.}
    \cventry{2014 First Semester}{Corrector Assistant}{Facultad de Ingeniería y Ciencias aplicadas}{Santiago}{}{Test and assigments checker of the course \textit{Tecnologías de la Web}.}
    \cventry{2009--2014}{Patrulla UAndes}{Departamento de Admisión y Promoción}{Universidad de los Andes}{Santiago}{Promoting University of los Andes in activities oriented to the future students.}